Papers I Love

### 2019-12-01 texts/dev/PapersILove.tex
.

\subsubsection{Data Structures}
\begin{enumerate}
	\item{Hashed and Hierarchical Timing Wheels: Data Structures for the Efficient Implementation of a Timer Facility\\ \url{https://web.archive.org/web/20130319034954/https://www.cs.columbia.edu/~nahum/w6998/papers/sosp87-timing-wheels.pdf}}
\item {Bitlist New Full-Text Index for Low Space Cost and Efficient Keyword Search\\
\url{http://www.vldb.org/pvldb/vol6/p1522-rao.pdf}}
\end{enumerate}

@@

\subsubsection{Computer Graphics}
\begin{enumerate}
	\item {Algorithm for computer control of a digital plotter by J. E. Bresenham\\\url{https://www.cse.iitb.ac.in/~paragc/teaching/2013/cs475/papers/bresenham_line.pdf}}
	\item {Bresenham's Algorithm\\
\url{http://graphics.idav.ucdavis.edu/education/GraphicsNotes/Bresenhams-Algorithm.pdf}}
	\item {Simplex noise demystified\\\url{http://webstaff.itn.liu.se/~stegu/simplexnoise/simplexnoise.pdf}}
\end{enumerate}

@@

\subsection{Linear Algebra}
\begin{enumerate}
	\item {Basic Linear Algebra Subprograms for Fortran Usage\\
\url{https://ntrs.nasa.gov/archive/nasa/casi.ntrs.nasa.gov/19780018835.pdf}}
\item {An Extended Set of FORTRAN Basic Linear Algebra Subprograms\\\url{http://www.ma.man.ac.uk/~sven/pubs/Level2BLAS-1-TOMS14-88.pdf}}
	\item{FLAME: Formal Linear Algebra Methods Environment\\
\url{http://tinyurl.com/ycxkmzw7}}
	\item{The Five Greatest Applications of Markov Chains\\
\url{http://langvillea.people.cofc.edu/MCapps7.pdf}}
\end{enumerate}

>>>>

\subsubsection{Data Structures}
\begin{enumerate}
	\item{Lists and why they are useful\\ \url{https://academic.oup.com/comjnl/article-pdf/7/4/278/1013051/7-4-278.pdf}}
	\item{Hashed and Hierarchical Timing Wheels: Data Structures for the Efficient Implementation of a Timer Facility\\ \url{https://web.archive.org/web/20130319034954/https://www.cs.columbia.edu/~nahum/w6998/papers/sosp87-timing-wheels.pdf}}
\item {Bitlist New Full-Text Index for Low Space Cost and Efficient Keyword Search\\
\url{http://www.vldb.org/pvldb/vol6/p1522-rao.pdf}}
\end{enumerate}

@@

\subsubsection{Computer Graphics}
\begin{enumerate}
	\item {Algorithm for computer control of a digital plotter by J. E. Bresenham\\\url{https://www.cse.iitb.ac.in/~paragc/teaching/2013/cs475/papers/bresenham_line.pdf}}
	\item {Bresenham's Algorithm\\
\url{http://graphics.idav.ucdavis.edu/education/GraphicsNotes/Bresenhams-Algorithm.pdf}}
	\item {Simplex noise demystified\\\url{http://webstaff.itn.liu.se/~stegu/simplexnoise/simplexnoise.pdf}}

	\item{Pose Space Deformation: A Unified Approach to Shape Interpolation and
		Skeleton-Driven Deformation \\\url{http://scribblethink.org/Work/PSD/PSD.pdf}}
\end{enumerate}

@@

\subsection{Linear Algebra}
\begin{enumerate}
	\item {Basic Linear Algebra Subprograms for Fortran Usage\\
\url{https://ntrs.nasa.gov/archive/nasa/casi.ntrs.nasa.gov/19780018835.pdf}}
\item {An Extended Set of FORTRAN Basic Linear Algebra Subprograms\\\url{http://www.ma.man.ac.uk/~sven/pubs/Level2BLAS-1-TOMS14-88.pdf}}
	\item{FLAME: Formal Linear Algebra Methods Environment\\
\url{http://tinyurl.com/ycxkmzw7}}
	\item{The Five Greatest Applications of Markov Chains\\
\url{http://langvillea.people.cofc.edu/MCapps7.pdf}}
	\item{Linear Algebra for Computer Vision \\\url{http://buzzard.ups.edu/courses/2014spring/420projects/math420-UPS-spring-2014-wills-computer-vision.pdf}}
\end{enumerate}
